Northern Pikeminnow Predation on Juvenile Chinook Salmon and Potential Impacts to Local Populations in the Upper Salmon River, Idaho

### 2021-12-22 analysis/paper/paper.Rmd
added TBs bio plot

```{r load-libraries}
library(tidyverse)
library(magrittr)
library(lubridate)
library(tidytable)
library(janitor)
library(purrr)
library(here)
library(FSA)
library(knitr)
library(kableExtra)
library(stringi)
library(english)

@@

>>>>

```{r load-libraries}
library(tidyverse)
library(magrittr)
library(lubridate)
library(tidytable)
library(janitor)
library(purrr)
library(here)
library(FSA)
library(knitr)
library(kableExtra)
library(stringi)
library(english)
library(lemon)
library(gridExtra)

@@

```{r bio-p, fig.cap = "Temp."}
spring_results$season = "Spring"
fall_results$season = "Fall"
bio_results = rbind(spring_results, fall_results)
bio_results$ymd = (ymd(bio_results$date))

pFish = bio_results %>%
  ggplot(aes(ymd, f50_g)) +
  geom_line(size = 1.15) +
  geom_ribbon(data = bio_results,
              aes(ymd,
                  ymin = f10_g,
                  ymax = f90_g),
              color = "grey65",
              alpha = 0.4) +
  theme_bw() +
  labs(y = "Cumulative fish consumed (g)",
       x = "",
       title = "") +
  facet_rep_wrap(~season,
                 scales = "free_x",
                 repeat.tick.labels = F) +
  theme(strip.background = element_rect(color = "white",
                                        fill = "white"),
        strip.text.x = element_text(size = 12),
        axis.text.x = element_blank(),
        axis.text.y = element_text(size = 11,
                                   color = "black"),
        axis.title.y = element_text(vjust = 1,
                                    size = 12),
        panel.grid.major.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.margin = unit(c(-.1, .3, -.3, .2), "cm"))

pTemp = bio_results %>%
  ggplot(aes(ymd, temperature_c)) +
  geom_line(color = "navyblue",
            size = 1.15) +
  theme_bw() +
  labs(y = expression("Water temperature"*~degree*C),
       x = "Month",
       title = "") +
  facet_rep_wrap(~season,
                 scales = "free_x",
                 repeat.tick.labels = F) +
  theme(strip.background = element_rect(color = "white",
                                        fill = "white"),
        strip.text.x = element_blank(),
        axis.text.x = element_text(size = 11,
                                   color = "black"),
        axis.title.x = element_text(size = 12),
        axis.text.y = element_text(size = 11,
                                   color = "black"),
        axis.title.y = element_text(vjust = 0.1,
                                    size = 12),
        panel.grid.major.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.margin = unit(c(-.1, .3, .1, .1), "cm"))

p_list = list(pFish, pTemp)
n_col = floor(sqrt(length(p_list)))

bio_p = do.call("grid.arrange",
                c(p_list, ncol = n_col))
